\documentclass[a4paper,11pt]{article}
\usepackage{amsmath,amssymb,hyperref,multicol,xcolor}
\usepackage[margin=1in]{geometry}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

%-------------------- HEADER --------------------%
\begin{center}
    {\LARGE \textbf{Juan Montoya Sanchez}} \\
    \vspace{1mm}
    Medellín, Colombia \\
    \href{mailto:montoyasanchezjuanjo@gmail.com}{montoyasanchezjuanjo@gmail.com} \\
    +57 300 366 8854
\end{center}

%-------------------- PROFILE --------------------%
\section*{Profile}
Enthusiastic Physics student deeply interested in High-Energy Physics (HEP). 
Hands-on experience in data analysis, software development (C++, Python), 
and collaborative research in an academic group affiliated with the CMS experiment at CERN. 
Keen to apply theoretical knowledge to real-world research projects 
and contribute to cutting-edge scientific discoveries.

%-------------------- EDUCATION --------------------%
\section*{Education}
\textbf{Universidad de Antioquia} \hfill 2019 -- \textit{Expected} 2026 \\
\textit{Bachelor of Physics} \\
GPA: 7.9/10

%-------------------- RESEARCH EXPERIENCE --------------------%
\section*{Research Experience}
\textbf{High-Energy Physics Group (GFIF), Universidad de Antioquia} \hfill 2023 -- Present 
\begin{itemize}
    \item Collaborate on low-$p_T$ ($<30$ GeV) $b$-jet analyses using C++ in conjunction with the CMS experiment at CERN.
    \item Implement data processing pipelines to study jet properties and improve event selection criteria.
    \item Investigate new strategies for tagging $b$-jets in high-luminosity collision data.
\end{itemize}

%-------------------- CONFERENCES & PRESENTATIONS --------------------%
\section*{Conferences \& Presentations}
\textbf{9\textsuperscript{th} Colombian Meeting on High Energy Physics (COMHEP)}, Pasto \hfill December 2024
\begin{itemize}
    \item \textit{Oral Presentation:} \textit{Estudio sistemático de la estructura de jets de $b$ y $\bar{b}$ a bajo $p_T$}.
\end{itemize}

\textbf{ICTP Physics Without Frontiers: Colombian Network for High Energy Physics School}, Ibagué \hfill November 30 -- December 2, 2023
\begin{itemize}
    \item Attended a specialized school focused on theoretical and experimental high-energy physics.
    \item Participated in workshops and lectures led by renowned international researchers.
\end{itemize}

\textbf{8\textsuperscript{th} Colombian Meeting on High Energy Physics (COMHEP)}, Ibagué \hfill December 4 -- 7, 2023 
\begin{itemize}
    \item Attended talks and discussions covering key topics in experimental and theoretical high-energy physics.
\end{itemize}

%-------------------- ADDITIONAL PROJECTS --------------------%
\section*{Additional Projects}
\textbf{United Nations Datathon 2024 -- Sustainable Tourism Analysis} \\
\href{https://github.com/JuanJ27/UN-Datathon-sisifos}{GitHub Link}
\begin{itemize}
    \item Analyzed large tourism datasets to highlight sustainability metrics.
    \item Created interactive data visualizations using Python libraries 
    (\texttt{geopandas}, \texttt{plotly}) for global insights.
\end{itemize}

\textbf{NASA International Space Apps Challenge 2024 -- Galactic Problem Solver} \\
\href{https://github.com/tonnysoyyo/NASA-Space-Apps}{GitHub Link}
\begin{itemize}
    \item Awarded the “Galactic Problem Solver” certificate for outstanding participation.
    \item Developed innovative data visualization techniques representing climate patterns using Python.
    \item Collaborated with a multidisciplinary team to address challenges in space and Earth-related contexts.
\end{itemize}

%-------------------- TUTORING EXPERIENCE --------------------%
\section*{Tutoring Experience}
\textbf{Tutor at Tutor.com} \hfill November 2024 -- Present
\begin{itemize}
    \item Provide online math and physics tutoring to students with diverse academic backgrounds.
    \item Tailor explanations to different learning styles, enhancing conceptual understanding.
\end{itemize}

%-------------------- SKILLS --------------------%
\section*{Skills}
\begin{multicols}{2}
\textbf{Programming:} 
\begin{itemize}
    \item C++ (HEP software, object-oriented design)
    \item Python (data analysis, visualization)
    \item Bash (basic automation, Linux environment)
    \item Julia (initial learning phase)
\end{itemize}

\columnbreak

\textbf{Tools:}
\begin{itemize}
    \item \LaTeX\ (scientific writing)
    \item Linux (Debian-based systems)
    \item ROOT (desirable for HEP data analysis, if applicable)
\end{itemize}

\textbf{Languages:}
\begin{itemize}
    \item English (B2)
    \item Spanish (Native)
\end{itemize}

\textbf{Soft Skills:}
\begin{itemize}
    \item Problem-solving
    \item Teamwork \& Collaboration
    \item Adaptability
\end{itemize}

\end{multicols}

%-------------------- END DOCUMENT --------------------%
\end{document}
